---
name: Myo Minn
surname: Oo
position: "MBBS, PhD"
# address: "B-852 Bannatyne Ave, Winnipeg, R3E0W5, MB, Canada"
address: "S303, 35 Rolling Mills Rd, Toronto, M5A 0V6, ON, CA"
phone: "+1 (437) 580-8121"
www: myominnoo.com
email: "dr.myominnoo@gmail.com"
github: myominnoo
linkedin: myominnoo
researchgate: Myo-Minn-Oo
orcid: 0000-0003-4089-016X
profilepic: "./img/myominnoo.jpg"
date: "`r format(Sys.time(), '%B %Y')`"
# headcolor: 009ACD # blue
headcolor: 990000 # crimson red
aboutme: "As an epidemiologist, I'm dedicated to global health and implementation science, focusing on reducing health disparities in underserved communities. I specialize in data science and automation to tackle real-world health challenges. Even this CV was compiled using code and a data-driven approach."
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: false
always_allow_html: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
library(vitae)

# get google scholar citations
gs_id <- "IWzz0rUAAAAJ"
pubs <- scholar::get_profile(gs_id)
```

# Education

```{r EDUCATION}
readxl::read_excel("data/data.xlsx", sheet = "education-details") %>% 
  detailed_entries(
    with = with,
    what = what,
    why = why,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )

```

# Research Interests

::: {.center data-latex=""}
Infectious Diseases (HIV/STBBI, TB, Malaria), Implementation Science, Health Service Research, Underserved Populations (Sex workers, gbMSM, Migrants, Indigenous Peoples).
:::

# Professional Experience

```{r EMPLOYMENT}
employment <- readxl::read_excel("data/data.xlsx", sheet = "employment")
employment %>%
  detailed_entries(
    with = with,
    what = what,
    why = why,
    when = glue::glue("{startMonth} {startYear} ---- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

# Grants, Awards, and Honors

```{r grant}
readxl::read_excel("data/data.xlsx", sheet = "grants-details") %>% 
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!-- \pagebreak -->

# Selected Publications

Since 2016, I have authored **`r scholar::get_num_articles(gs_id)` research papers**. Some highlights are listed below, with citations taken from Google Scholar on `r format(Sys.time(), "%e %B %Y")`. My **h-index** is **`r pubs$h_index`** with total citations of `r pubs$total_cites`. 

For a complete list of publications, see [*my Google Scholar profile*](https://scholar.google.com/citations?hl=en&user=IWzz0rUAAAAJ).

```{r SELECTED PUBLICATIONS}
# Read any bib files
vitae::bibliography_entries("bib/selected.bib") %>% 
  mutate(year = lubridate::year(as.Date(issued))) %>% 
  arrange(-year)
```

## Books

```{r books}
# Read any bib files
vitae::bibliography_entries("bib/books.bib") 
```

## R packages

```{r RPackages}
# Read any bib files
vitae::bibliography_entries("bib/rpackages.bib") 
```


# Works in progress

```{r under reviews}
# Read any bib files
vitae::bibliography_entries("bib/underreviews.bib")
```

# Projects

```{r projects}
vitae::bibliography_entries("bib/projects.bib")
```

# Data Science Products

```{r dev}
readxl::read_excel("data/data.xlsx", sheet = "programming") %>%  
  mutate(link = ifelse(is.na(link), link, 
                       paste0("\\href{", link, "}{\\faLink}")), 
         github = ifelse(is.na(github), github, 
                         paste0("\\href{", github, "}{\\faGithub}"))) %>% 
  detailed_entries(with = sum, what = lang, where = link, 
                   why = why, when = github, .protect=FALSE)  
```

# Presentations

```{r presentations}
readxl::read_excel("data/data.xlsx", sheet = "presentations") %>% 
  vitae::detailed_entries(what, when, with, where, why)
```

# Teaching

```{r teaching}
readxl::read_excel("data/data.xlsx", sheet = "teaching") %>% 
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Services & Outreach

```{r services, results='asis', width = 40000}
skills_formatted <- readxl::read_excel(
    "data/data.xlsx", sheet = "services"
) %>% 
  mutate(skill = if_else(is.na(details)|details=="", 
                         glue::glue("{skill}"), 
                         glue::glue("{skill} ({details})"))) %>% 
  group_by(group) %>% 
  summarize(skills = glue::glue_collapse(skill, sep = " $\\bullet$ "))

for (group in skills_formatted$group) {
  cat(
    glue::glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```


# Skills

```{r skills, results='asis', width = 40000}
skills_formatted <- readxl::read_excel(
    "data/data.xlsx", sheet = "skills-details"
) %>% 
  mutate(skill = if_else(is.na(details)|details=="", 
                         glue::glue("{skill}"), 
                         glue::glue("{skill} ({details})"))) %>% 
  arrange(group) %>% 
  group_by(group) %>% 
  summarize(skills = glue::glue_collapse(skill, sep = " $\\bullet$ "))

for (group in skills_formatted$group) {
  cat(
    glue::glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```


<!-- \pagebreak -->

# Online Tutorials

1. [Create Publication-Ready Tables using `gtsummary`](https://www.youtube.com/watch?v=kDyzBYx6CVs&list=PLopxIleZRP2auz5v1VjiF68_Urbb_rTFC&ab_channel=DataRecap)
2. [R Webinars](https://www.youtube.com/watch?v=XJ9iNVYp7R8&list=PLopxIleZRP2aV-dnbkZs2eydbdWD0IXSf&ab_channel=DataRecap)
3. [Statistics & Public Health Webinars](https://www.youtube.com/watch?v=O7lIWWZTbmI&list=PLopxIleZRP2ZUit_7Ag-PMugAV8dBavYA&ab_channel=DataRecap)
4. [Git & GitHub Basics](https://www.youtube.com/watch?v=JEuMqcPdJRo&list=PLopxIleZRP2agpuMKrbwEyYMSi9jhjUo4&ab_channel=DataRecap)
5. [Making infographics using MS PowerPoint](https://www.youtube.com/watch?v=Zzs9epH_AK8&list=PLopxIleZRP2bdEAV3eureiDo5etA_AR9k&ab_channel=DataRecap)
6. [Data entry using EpiData Manager & EntryClient](https://www.youtube.com/watch?v=WEKBQGcndoc&list=PLopxIleZRP2Zr8t4HmB1vy-vZQht0BBdM&ab_channel=DataRecap)
7. [Introdution to R and RStudio](https://www.youtube.com/watch?v=q9LJsymvb_g&list=PLopxIleZRP2bdEXiq5Zzv8HhTiYsUgdYb&ab_channel=DataRecap)
8. [Statistics with R - ENGLISH Version](https://www.youtube.com/watch?v=S-RTBqP7O7o&list=PLopxIleZRP2b8peVo5K8KuCo5Yo_yk4Is&ab_channel=DataRecap)
9. [Statistics with R - MYANMAR Version](https://www.youtube.com/watch?v=LR9b0rWh7GU&list=PLopxIleZRP2YZ-B5gAuxARnoleZMeXyjk&ab_channel=DataRecap)


# Charting the Course: Reflecting on My Journey Thus Far

```{r JOURNEY, fig.align='center', fig.width=6.5, fig.height=2.7, fig.showtext=TRUE}
emojifont::load.fontawesome()
uni <- emojifont::fontawesome('fa-university')
work <- emojifont::fontawesome('fa-briefcase')
vacation <- emojifont::fontawesome('fa-plane')

world <- rnaturalearth::ne_countries("medium", returnclass = 'sf')
cities_geom <- sf::st_sfc(
  sf::st_point(c(95, 23)),
  sf::st_point(c(85, 27)),
  sf::st_point(c(78, 25)),
  sf::st_point(c(81, 7)),
  sf::st_point(c(100, 17)),
  sf::st_point(c(105, 17)),
  sf::st_point(c(120, 32)),
  sf::st_point(c(105, 2)),
  sf::st_point(c(110, -7)),
  sf::st_point(c(10, 47)),
  sf::st_point(c(144, -6)), 
  sf::st_point(c(120, 17)),
  sf::st_point(c(38, 1)), 
  sf::st_point(c(-90, 50.5))
) 
cities = sf::st_sf(
  geometry = cities_geom
) |>
  sf::st_set_crs(4326) |>
  mutate(
    label = c(
      paste(work, uni, sep = " "),
      rep(work, 3), 
      uni, 
      vacation, 
      vacation, 
      vacation, 
      vacation, 
      work, 
      work, 
      vacation, 
      work, 
      work
    )
  )

routes = cities |> 
  sfnetworks::as_sfnetwork() |> 
  sf::st_as_sf('edges') |> 
  sf::st_segmentize(units::set_units(100, m))
ggplot() +
  geom_sf(data = world, color = 'white', lwd = 0.1) +
  geom_sf_text(
    data = cities,
    aes(label = label),
    size = 2.5,
    # color = '#009ACD',
    color = '#990000',
    family = "fontawesome-webfont"
  ) +
  geom_sf(
    data = routes,
    # color = '#009ACD',
    color = '#990000',
    size = 0.5, alpha = 0.5,
    linetype = 'dotted'
  ) +
  coord_sf(
    crs = '+proj=robin',
    xlim = c(-9e6, 13e6),
    ylim = c(-4e6, 7e6)
  ) +
  theme_void() +
  theme(
    plot.margin = margin(-1, 0, -0.5, 0, "cm")
  )
```
This figure is created using the packages, `rnaturalearth`, `sf`, `sfnetworks`, `emojifont`, and `ggplot2`.

# References 

```{r REFERENCES}
readxl::read_excel("data/data.xlsx", sheet = "references") %>% 
  detailed_entries(
    with = with,
    what = what,
    why = why,
    when = when,
    where = where
  )

```

# Note

This document is written in `rmarkdown` and generated using `vitae` package and `awesome-cv` template. All the source code behind this `CV` is available on this \href{https://github.com/myominnoo/CV}{GitHub repo}.

