---
graphics: yes
name: Myo Minn
surname: Oo
headcolor: 414141
# qualifications: "MBBS, Ph.D."
position: "MBBS, Ph.D."
address: "Homate St., North Goroka, EHP 441, Papua New Guinea"
phone: "+675 7493 9800"
www: myominnoo.github.io
email: "myo.minnoo@swisstph.ch"
github: myominnoo
linkedin: myominnoo
researchgate: Myo-Minn-Oo
orcid: 0000-0003-4089-016X
aboutme: |
  https://www.swisstph.ch/fr/staff/profile/people/myo-minn-oo/
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa6-cv.csl"
nocite: "@*"
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[R]{\thepage}
knit: bookdown::render_book
bibliography_selected: "bib/selected.bib"
bibliography_rpackages: "bib/rpackages.bib"
bibliography_books: "bib/books.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(ezpickr)
library(glue)
```

# EDUCATION

```{r education}
ezpickr::pick("data/education.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# RESEARCH

::: {.center data-latex=""}
Infectious Disease Epidemiology, Modelling, Health Systems Research, Research Methods

Operational Research, Sexual & Reproductive Health, Aging and Chronic Diseases.
:::

```{r research-experience}
ezpickr::pick("data/research-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# GRANTS AND HONORS

```{r grant}
ezpickr::pick("data/grant.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```
# WORKS IN PROGRESS

```{r works in progress}
ezpickr::pick("data/works-in-progress.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# PRESENTATIONS

```{r presentations}
ezpickr::pick("data/presentations.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# PUBLICATIONS

<!-- ## Selected Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_selected}
:::
\endgroup -->

## Selected Publications

::: {.center data-latex=""}
Full List of 30+ research outputs on Google Scholar: https://scholar.google.com/citations?user=IWzz0rUAAAAJ&hl=en
:::

::: {#refs_selected}
:::

## Books

::: {#refs_books}
:::

## R Packages

::: {#refs_rpackages}
:::

# TEACHING

```{r teaching}
ezpickr::pick("data/teaching-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# SKILLS

```{r}
skills_formatted <- ezpickr::pick("data/skills.xlsx") %>% 
  mutate(skill = if_else(is.na(details)|details=="", glue("{skill}"), glue("{skill} ({details})"))) %>% 
  group_by(group) %>% 
  summarize(skills = glue_collapse(skill, sep = " $\\bullet$ "))
```

```{r, results='asis', width = 40000}
for (group in skills_formatted$group) {
  cat(
    glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```


# SERVICES

```{r}
skills_formatted <- ezpickr::pick("data/services.xlsx") %>% 
  mutate(skill = if_else(is.na(details)|details=="", glue("{skill}"), glue("{skill} ({details})"))) %>% 
  group_by(group) %>% 
  summarize(skills = glue_collapse(skill, sep = " $\\bullet$ "))
```

```{r, results='asis', width = 40000}
for (group in skills_formatted$group) {
  cat(
    glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```


# Note

This document is written in rmarkdown and auto-generated using vitae package and custom LaTeX template from \href{https://github.com/seabbs/cv}{Sam Abott}. All the source code behind this CV is available on this \href{https://github.com/myominnoo/CV}{GitHub repo}.

