---
name: Myo Minn
surname: Oo
position: "MBBS, Ph.D."
pronouns: he/him
github: myominnoo
linkedin: myominnoo
researchgate: Myo-Minn-Oo
orcid: 0000-0003-4089-016X
profilepic: "data/myominnoo.jpg"
date: "`r format(Sys.time(), '%d %B %Y')`"
headcolor: 990000 # crimson red
aboutme: "An Epidemiologist, Implementation Scientist, Global Health Researcher with expertise in STBBI/HIV, underserved populations, health equity gaps through robust methodogical frameworks and ethical lens. Skilled in R programming and data product development."
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: false
always_allow_html: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)

# get google scholar citations
gs_id <- "IWzz0rUAAAAJ"
pubs <- scholar::get_profile(gs_id)

```

# Research Interests

::: {.center data-latex=""}
STBBI/HIV (in Sex workers, gbMSM), Implementation Science, Health Services Research (in Underserved Populations - Migrants, Indigenous Peoples), Global Health System, Data Science, HEOR.


:::

# Work/Research Experiences

```{r}
readxl::read_excel("data/main-data.xlsx", sheet = "employment") |> 
  detailed_entries(what, when, with, where, why)
```


<!-- # Grants, Awards, and Honors -->

<!-- ```{r grant} -->
<!-- readxl::read_excel("data/main-data.xlsx", sheet = "grants") %>%  -->
<!--   tidyr::fill(-why) %>% -->
<!--   vitae::detailed_entries(what, when, with, where, why) -->
<!-- ``` -->


# Education

```{r}
library(tibble)
readxl::read_excel("data/main-data.xlsx", sheet = "education") |> 
  detailed_entries(what, when, with, where, why)
```


# Publications

Since 2016, I have authored **`r scholar::get_num_articles(gs_id)` peer-reviewed articles**. As of `r format(Sys.time(), "%e %B %Y")`, my work has an **h-index** of **`r pubs$h_index`** and a total of `r pubs$total_cites` citations, according to Google Scholar. See [*my Google Scholar profile*](https://scholar.google.com/citations?hl=en&user=IWzz0rUAAAAJ).

<!-- ## Peer-reviewed articles -->

<!-- ```{r} -->
<!-- bibliography_entries("data/publications.bib") |> -->
<!--     dplyr::mutate(year = lubridate::year(as.Date(issued))) |> -->
<!--     dplyr::arrange(desc(year)) -->
<!-- ``` -->

<!-- ## Submitted -->
<!-- ```{r} -->
<!-- bibliography_entries("data/publications_submitted.bib") -->
<!-- ``` -->

<!-- # ## Books -->
<!-- #  -->
<!-- # ```{r} -->
<!-- # vitae::bibliography_entries("data/books.bib")  -->
<!-- ``` -->



<!-- # Data Projects -->

<!-- ```{r} -->
<!-- readxl::read_excel("data/main-data.xlsx", sheet = "products") |>  -->
<!--   dplyr::mutate( -->

<!--     where = ifelse(is.na(where), where,  -->
<!--                        paste0("\\href{", where, "}{\\faLink}")),  -->

<!--     when = ifelse(is.na(when), when,  -->
<!--                          paste0("\\href{", when, "}{\\faGithub}")),  -->
<!--     with = paste0(with, " | ", what),  -->
<!--   ) |>  -->
<!--   detailed_entries(what = why, with = with, where = where,  -->
<!--                    when = when, .protect=FALSE)   -->
<!-- ``` -->



<!-- # Presentations -->

<!-- ```{r presentations} -->
<!-- readxl::read_excel("data/main-data.xlsx", sheet = "presentations") %>%  -->
<!--   vitae::detailed_entries(what, when, with, where, why) -->
<!-- ``` -->

<!-- # Mentorship and teaching experiences -->

<!-- ```{r teaching} -->
<!-- readxl::read_excel("data/main-data.xlsx", sheet = "teaching") %>%  -->
<!--   tidyr::fill(-why) %>% -->
<!--   vitae::detailed_entries(what, when, with, where, why) -->
<!-- ``` -->


# Academic and Research Services

```{r services, results='asis', width = 40000}
skills_formatted <- readxl::read_excel(
    "data/main-data.xlsx", sheet = "services"
) |> 
  dplyr::mutate(skill = dplyr::if_else(is.na(details)|details=="", 
                         glue::glue("{skill}"), 
                         glue::glue("{skill} ({details})"))) |>  
  dplyr::group_by(group) |> 
  dplyr::summarize(skills = glue::glue_collapse(skill, sep = " $\\bullet$ "))

for (group in skills_formatted$group) {
  cat(
    glue::glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    dplyr::filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```


# Skills

```{r skills, results='asis', width = 40000}
skills_formatted <- readxl::read_excel(
    "data/main-data.xlsx", sheet = "skills"
) |> 
  dplyr::mutate(skill = dplyr::if_else(is.na(details)|details=="", 
                         glue::glue("{skill}"), 
                         glue::glue("{skill} ({details})"))) |> 
  dplyr::arrange(group) |> 
  dplyr::group_by(group) |> 
  dplyr::summarize(skills = glue::glue_collapse(skill, sep = " $\\bullet$ "))

for (group in skills_formatted$group) {
  cat(
    glue::glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    dplyr::filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```


<!-- # Online Tutorials -->

<!-- 1. [Create Publication-Ready Tables using `gtsummary`](https://www.youtube.com/watch?v=kDyzBYx6CVs&list=PLopxIleZRP2auz5v1VjiF68_Urbb_rTFC&ab_channel=DataRecap) -->
<!-- 2. [R Webinars](https://www.youtube.com/watch?v=XJ9iNVYp7R8&list=PLopxIleZRP2aV-dnbkZs2eydbdWD0IXSf&ab_channel=DataRecap) -->
<!-- 3. [Statistics & Public Health Webinars](https://www.youtube.com/watch?v=O7lIWWZTbmI&list=PLopxIleZRP2ZUit_7Ag-PMugAV8dBavYA&ab_channel=DataRecap) -->
<!-- 4. [Git & GitHub Basics](https://www.youtube.com/watch?v=JEuMqcPdJRo&list=PLopxIleZRP2agpuMKrbwEyYMSi9jhjUo4&ab_channel=DataRecap) -->
<!-- 5. [Making infographics using MS PowerPoint](https://www.youtube.com/watch?v=Zzs9epH_AK8&list=PLopxIleZRP2bdEAV3eureiDo5etA_AR9k&ab_channel=DataRecap) -->
<!-- 6. [Data entry using EpiData Manager & EntryClient](https://www.youtube.com/watch?v=WEKBQGcndoc&list=PLopxIleZRP2Zr8t4HmB1vy-vZQht0BBdM&ab_channel=DataRecap) -->
<!-- 7. [Introdution to R and RStudio](https://www.youtube.com/watch?v=q9LJsymvb_g&list=PLopxIleZRP2bdEXiq5Zzv8HhTiYsUgdYb&ab_channel=DataRecap) -->
<!-- 8. [Statistics with R - ENGLISH Version](https://www.youtube.com/watch?v=S-RTBqP7O7o&list=PLopxIleZRP2b8peVo5K8KuCo5Yo_yk4Is&ab_channel=DataRecap) -->
<!-- 9. [Statistics with R - MYANMAR Version](https://www.youtube.com/watch?v=LR9b0rWh7GU&list=PLopxIleZRP2YZ-B5gAuxARnoleZMeXyjk&ab_channel=DataRecap) -->


<!-- # References  -->

<!-- ```{r REFERENCES} -->
<!-- readxl::read_excel("data/main-data.xlsx", sheet = "references") |>  -->
<!--   dplyr::mutate(with = paste0(with, " | ", why)) |>  -->
<!--   detailed_entries( -->
<!--     with = with, -->
<!--     what = what, -->
<!--     when = when, -->
<!--     where = where -->
<!--   ) -->

<!-- ``` -->

# Note

This CV is written in `RMarkdown` and generated using the `vitae` package with the `awesome-cv` template. The complete source code is available on my \href{https://github.com/myominnoo/CV}{GitHub repository}.
